First Order Logic of Sparse Random Hyper-Graphs

### 2019-07-08 Presentacion/Presentación.tex
Mas dibus

\documentclass[handout, 11pt]{beamer}

@@

\author{L\'azaro Alberto Larrauri Borroto \\ 
	Supervisor: Marc Noy Serrano}

@@

\begin{document}
	\frame{\titlepage}
	\frame{\tableofcontents}

@@

>>>>

\documentclass[11pt]{beamer}

@@

\author{L\'azaro Alberto Larrauri Borroto}

@@

\begin{document}
\begin{frame}[plain]
	\maketitle
	\small
	\begin{center}
	Supervisor: Marc Noy Serrano
	\end{center}

\end{frame}
	\frame{\tableofcontents}

@@

	\begin{frame}{The $k$-morphism relation for graphs}
		To make the definitions suitable for proofs using E.F. games we need to work with "graphs
		with constants". 
		\begin{definition}
			The center of a connected graph $G(\clist)$ is its minimal 
			connected subgraph containing all the constants and clusters.\\
			\vspace{0.2 em} If $G(\clist)$
			is not connected its center is the union of the centers of its connected
			components.   
		\end{definition}
	\end{frame}

	\begin{frame}{The $k$-morphism relation for graphs}
	A sketch of a center:
	\begin{center}
		\includegraphics[width=0.5\linewidth]{Center.pdf}
	\end{center}
	\end{frame}

	\begin{frame}{The $k$-morphism relation for graphs}
	\begin{definition} 
		We say that$G_1(\clist)\morph{k}G_2(\clist)$, if there is an isomorphism
		$f:Center(G_1)\rightarrow Center(G_2)$ s.t.
		\begin{itemize}
			\item $f(c^1_i)=c^2_i$ for all constants, and
			\item $Tree(x,G_1)\morph{k} Tree(f(x),G_2)$ for all $x\in V(Center(G_1))$.
		\end{itemize}
	\end{definition}

	\begin{frame}{The $k$-morphism relation for graphs}
	\begin{center}
		\includegraphics[width=\linewidth]{kmorphiccenter1.pdf}
	\end{center}
	\end{frame}

	\begin{frame}{The $k$-morphism relation for graphs}
	\begin{center}
		\vspace{0.58 em}
		\includegraphics[width=\linewidth]{kmorphiccenter2.pdf}
	\end{center}
	\end{frame}

	\begin{frame}{The $k$-morphism relation for graphs}
	\begin{center}
	\vspace{1.6em}
	\includegraphics[width=\linewidth]{kmorphiccenter3.pdf}
	\end{center}
	\end{frame}

	\begin{frame}{The $k$-morphism relation for graphs}
		Connected $k$-morphic graphs $G,H$ with $L(G),L(H)\leq 0$ have the same
		first order rank $k$-type.	\\~\\

		The tool for proving this are Ehrenfeucht Fraisse games.
		\\~\\

		The $k$-morphism relation gives, for any $r$, a finite classification of the cycles of diameter
		at most $r$ with trees of radii at most $r$ hanging from their vertices.
